Manuscript Figures for Genome Biology

### 2018-09-07 manuscript_figures/manuscript_figures.Rmd
Add TPRs to Figure S1

plist <- vector("list", length(resfile))
tab <- NULL
for (l in seq_along(resfile)){

  de5 <- readRDS(file=resfile[l])
  res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))
  res5d$es_dist <- labs2[l]
  res5d$pi0 <- labs[l]
  tab <- rbind(tab, res5d)
}

@@

@@

leg <- get_legend(FigStrong)
Fig <- plot_grid(FigStrong + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                 FigWeak + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2, 
                 labels = paste0(LETTERS[1:2], "       ",
                          c("Strongly informative covariate",
                            "Weakly informative covariate")),
                 hjust = 0)
plot_grid(Fig, leg, ncol=2, rel_widths = c(1,0.1))
ggsave(file.path(outdir, "Figure_yeast_varyingpi0.pdf"), width=10, height=6.5)

>>>>

plist <- vector("list", length(resfile))
tab <- NULL
for (l in seq_along(resfile)){
  de5 <- readRDS(file=resfile[l])
  res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))
  res5d$es_dist <- labs2[l]
  res5d$pi0 <- labs[l]
  tab <- rbind(tab, res5d)
}

@@

FigStrongT <- plotsim_average(tab, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE, grpVars = c("es_dist", "pi0")) +
                ggtitle("") +
  ylim(0,0.88) +
  facet_grid( ~ es_dist + pi0) 
FigStrongT

@@

FigWeakT <- plotsim_average(tab, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE, grpVars = c("es_dist", "pi0")) +
                ggtitle("") +
  ylim(0,0.88) +
  facet_grid( ~ es_dist + pi0)
FigWeakT

leg <- get_legend(FigStrong)

FigA <- plot_grid(FigStrong + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigStrongT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2)

FigB <- plot_grid(FigWeak + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigWeakT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2)

Fig <- plot_grid(FigA, FigB,
                 nrow = 2, 
                 labels = paste0(LETTERS[1:2], "       ",
                          c("Strongly informative covariate",
                            "Weakly informative covariate")),
                 hjust = 0)
plot_grid(Fig, leg, ncol=2, rel_widths = c(1,0.1))
ggsave(file.path(outdir, "Figure_yeast_varyingpi0.pdf"), width=10, height=12)
